Winter weather on exam dates and matriculation for a prestigious university in Japan

### 2021-05-12 Slides/todai_center.tex
Revised slides for presentation

\begin{frame}\frametitle{Research Question \& Roadmap}
  \begin{itemize}
    \item Research Question: Does cold weather on the exam dates worsens performance at a high-stakes exam?
    \item Roadmap:
      \begin{itemize}
        \item Background
        \item Data
        \item Empirical strategy
        \item Results
        \item (Some more results not in the paper for now)
      \end{itemize}
    \item A quick heads-up\dots
      \begin{itemize}
        \item Planning to submit the paper to JEEM short 
        \item Max 3,000 words (but ``modestly longer papers will be considered'')
        \item My paper now has 3,200 words
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Background - Center Test}
  \begin{itemize}
    \item In Japan, for public university admission, students need to take two exams:
    \item First-stage: \textcolor{red}{Center Test}
      \begin{itemize}
        \item Held in mid-January (Saturday and Sunday)
          \begin{itemize}
            \item Social science, Japanese, and English on the first day (9:30 AM - 6:10 PM)
            \item Mathematics and natural science on the second day (9:30 AM - 5:50 PM)
          \end{itemize}
        \item Questions are multiple-choice and common for all exam takers
        \item Students take the exam in their own prefectures
      \end{itemize}
    \item Second-stage: University-specific exams
      \begin{itemize}
        \item Typically held in late February
        \item Students take the exams at universities they apply for
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Empirical Strategy - Why UTokyo?}
  \begin{itemize}
    \item Suppose that low temperature negatively affects exam performance
    \item If I consider a matriculation for a middle-ranked university,
      \begin{enumerate}
        \item students in the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
        \item students in the prefecture who would get into a higher-ranked university may get into the middle-ranked university
      \end{enumerate}
    \item Considering the matriculation for UTokyo (= the most prestigious university in Japan) rules out the second possibility
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Empirical Strategy - Estimation equation}
  \label{est_eq}
  \begin{equation*}
    Y_{jt} = \sum_k \alpha_k T_{jt}^k + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
  \end{equation*}
  \begin{itemize}
    \item $Y_{jt}$: matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$
    \item $T_{jt}^k$: bin of average temperature across two exam dates in $j$ in year $t$
    \item $X_{jt}$: other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates
    \item $\mu_j$: prefecture fixed effects
    \item $\tau_t$: year fixed effects
    \item $\epsilon_{jt}$: error term
    \item Standard errors are clustered at the prefecture level 
  \end{itemize}
  \hyperlink{temp_dev_1}{\beamergotobutton{Temperature variation}}
  \hyperlink{temp_dev_2}{\beamergotobutton{Within-prefecture temperature variation}}
\end{frame}

\begin{frame}\frametitle{Temperature effects on the matriculation shares (\%)}
  \begin{center}
    \begin{figure}
      \includegraphics[width=6.5cm]{../Output/images/main_reg_2.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        The figure shows the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
        I use temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test.
        Each interval on the x-axis does not include the right end.
        The 90\% confidence intervals are shown.
        Prefecture fixed effects and year fixed effects are also included.
        Standard errors are clustered at the prefecture level.
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Effects of other weather variables on the matriculation shares (\%)}
    \begin{table}[h]
      \Wider[4em]{
      \center
      \fontsize{6}{7}\selectfont
      \input{../Output/tex/main_reg_beamer.tex}
      \tiny
      \begin{tablenotes}
      \item 
        The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
        The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
        I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
        Standard errors are clustered at the prefecture level.
      \end{tablenotes}
    }
    \end{table}
\end{frame}

@@

\begin{frame}\frametitle{Cognitive performance at the exam vs. Preparation}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Temperature at the exam dates
    \end{center}
    \begin{figure}[h]
      \centering
      \includegraphics[width = \textwidth]{../Output/images/reg_pre10_exam_4.pdf}
    \end{figure}
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Average temperature for 10 days before the exam
    \end{center}
    \begin{figure}[h]
      \includegraphics[width = \textwidth]{../Output/images/reg_pre10_pre10_4.pdf}
      \centering
    \end{figure}
  \end{minipage}
  \tiny
  \begin{tablenotes}
  \item Notes;
    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
    In the left figure, the estimates on the temperature on the exam dates are shown.
    In the right figure, the estimates on the average temperature for 10 days before the exam are shown.
    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
    Each interval on the x-axis does not include the right end.
    The 90\% confidence intervals are shown.
    Prefecture fixed effects and year fixed effects are also included.
    Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{frame}

\begin{frame}\frametitle{Effects of other weather variables on the matriculation shares (\%)}
  \begin{table}[h]
    \Wider[4em]{
    \center
    \fontsize{7}{5}\selectfont
    \input{../Output/tex/reg_pre10_beamer.tex}
    \tiny
    \begin{tablenotes}
    \item 
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      Standard errors are clustered at the prefecture level.
    \end{tablenotes}
  }
  \end{table}
\end{frame}

\begin{frame}\frametitle{Some additional analysis: Female vs. Male}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Female \\
      (mean: 0.38 \%, median: 0.13 \%)
    \end{center}
    \begin{figure}[h]
      \centering
      \includegraphics[width = \textwidth]{../Output/images/reg_gender_2.pdf}
    \end{figure}
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Male \\
      (mean: 1.70 \%, median: 0.61 \%)
    \end{center}
    \begin{figure}[h]
      \includegraphics[width = \textwidth]{../Output/images/reg_gender_4.pdf}
      \centering
    \end{figure}
  \end{minipage}
  \tiny
  \begin{tablenotes}
  \item Notes;
    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
    In the left figure, the outcome is the matriculation share of female students from each prefecture.
    In the right figure, the outcome is the matriculation share of male students from each prefecture.
    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
    Each interval on the x-axis does not include the right end.
    The 90\% confidence intervals are shown.
    Prefecture fixed effects and year fixed effects are also included.
    Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{frame}

\begin{frame}\frametitle{Some additional analysis: Humanity vs. Science}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Humanity \\
      (mean: 2.07 \%, median: 0.76 \%)
    \end{center}
    \begin{figure}[h]
      \centering
      \includegraphics[width = \textwidth]{../Output/images/reg_major_2.pdf}
    \end{figure}
  \end{minipage}
  \begin{minipage}{0.49\textwidth}
    \begin{center}
      Science \\
      (mean: 2.09 \%, median: 0.76 \%)
    \end{center}
    \begin{figure}[h]
      \includegraphics[width = \textwidth]{../Output/images/reg_major_4.pdf}
      \centering
    \end{figure}
  \end{minipage}
  \tiny
  \begin{tablenotes}
  \item Notes;
    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
    In the left figure, the outcome is the matriculation share to humanity major from each prefecture.
    In the right figure, the outcome is the matriculation share to science major from each prefecture.
    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
    Each interval on the x-axis does not include the right end.
    The 90\% confidence intervals are shown.
    Prefecture fixed effects and year fixed effects are also included.
    Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{frame}

\begin{frame}\frametitle{Conclusion}
  \begin{itemize}
    \item Weather on the exam dates affects the matriculations for UTokyo
      \begin{itemize}
        \item Reducing temperature from 3-6 \degree C to $<$0 \degree C decreases the probability of matriculation by 0.18 percentage point \\
          (9\% of the average and 22\% of the median matriculation shares)
        \item Snow on the ground cumulated more than 10cm decreases the probability of matriculation by 0.11 percentage point \\
          (5\% of the average and 13\% of the median matriculation shares)
      \end{itemize}
    \item Suggests that the exam performance is negatively affected by winter weather
    \item Implications for university admission process:
      \begin{itemize}
        \item Use other information such as extracurricular activities and personal statements for university admission?
        \item Adjust weights for Center Test and the second-stage exam?
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Deviation of temperatures from within-prefecture averages}
  \label{temp_dev_2}
  \begin{center}
    \begin{figure}
      %\caption{Map of matriculation shares (\%)}
      \includegraphics[width=6.6cm]{../Output/images/temperature_diff_by_year.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
        Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
        In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right). \\
      \item 
        \hyperlink{est_eq}{\beamergotobutton{Estimation equation}}
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

>>>>

\begin{frame}\frametitle{Research Question \& Roadmap}
  \begin{itemize}
    \item Research Question: Does cold weather on the exam date worsen performance in a high-stakes exam?
    \item Roadmap:
      \begin{itemize}
        \item Background
        \item Data
        \item Empirical strategy
        \item Results
        \item (Some more results not in the paper for now)
      \end{itemize}
    \item A quick heads-up\dots
      \begin{itemize}
        \item Planning to submit the paper to JEEM short 
        \item Max 3,000 words (but ``modestly longer papers will be considered'')
        \item My paper now has 3,200 words
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Background - Center Test}
  \begin{itemize}
    \item In Japan, for public university admission, students need to take two exams:
    \item First-stage: \textcolor{red}{Center Test}
      \begin{itemize}
        \item Held in mid-January (Saturday and Sunday)
          \begin{itemize}
            \item Social science, Japanese, and English on the first day (9:30 AM - 6:10 PM)
            \item Mathematics and natural science on the second day (9:30 AM - 5:50 PM)
          \end{itemize}
        \item Questions are multiple-choice and common for all exam takers
        \item Students take the exam in their own prefectures
      \end{itemize}
    \item Second-stage: University-specific exams
      \begin{itemize}
        \item Universities hold exams typically in \textcolor{red}{late February} and/or mid-March
        \item Students take the exams at universities they apply for
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Empirical Strategy - Why UTokyo?}
  \begin{itemize}
    \item Suppose that low temperature negatively affects exam performance
    \item If I consider a matriculation for a middle-ranked university,
      \begin{enumerate}
        \item students in the prefecture who would have gotten into the middle-ranked university if the temperature were higher may end up in a lower-ranked university instead, but
        \item students in the prefecture who would have gotten into a higher-ranked university may end up in the middle-ranked university instead
      \end{enumerate}
    \item Considering matriculation for UTokyo (the most prestigious university in Japan) rules out the second possibility
  \end{itemize}
\end{frame}

\begin{frame}\frametitle{Empirical Strategy - Estimation equation}
  \label{est_eq}
  \begin{equation*}
    Y_{jt} = \sum_k \alpha_k T_{jt}^k + X_{jt}' \beta + \mu_j + \tau_t + \epsilon_{jt}.
  \end{equation*}
  \begin{itemize}
    \item $Y_{jt}$: matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$
    \item $T_{jt}^k$: $k$'th temperature interval 
      \begin{itemize}
        \item 3-$\degree$C intervals
        \item Average across two exam dates in $j$ in year $t$
      \end{itemize}
    \item $X_{jt}$: other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates
    \item $\mu_j$: prefecture fixed effects
    \item $\tau_t$: year fixed effects
    \item $\epsilon_{jt}$: error term
    \item Standard errors are clustered at the prefecture level 
  \end{itemize}
  \hyperlink{temp_dev_1}{\beamergotobutton{Temperature variation}}
  \hyperlink{temp_dev_2}{\beamergotobutton{Within-prefecture temperature variation}}
\end{frame}

\begin{frame}\frametitle{Temperature effects on the matriculation shares (\%) \\ {\small Low temperature negatively affects exam performance}}
  \begin{center}
    \begin{figure}
      \includegraphics[width=6.5cm]{../Output/images/main_reg_2.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        The figure shows the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
        I use temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test.
        Each interval on the x-axis does not include the right end.
        The 90\% confidence intervals are shown.
        Prefecture fixed effects and year fixed effects are also included.
        Standard errors are clustered at the prefecture level.
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{{\normalsize Effects of other weather variables on the matriculation shares (\%)} \\ {\small Cumulated snow on the ground negatively affects exam performance}}
    \begin{table}[h]
      \Wider[4em]{
      \center
      \fontsize{6}{7}\selectfont
      \input{../Output/tex/main_reg_beamer.tex}
      \tiny
      \begin{tablenotes}
      \item 
        The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
        The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
        I use weather variables at prefecture capitals between 6 AM and 6 PM on days of Center Test.
        Standard errors are clustered at the prefecture level.
      \end{tablenotes}
    }
    \end{table}
\end{frame}

@@

\begin{frame}\frametitle{Cognitive performance at the exam vs. Preparation \\ {\small Temperature on the exam date matters}}
  \begin{minipage}{0.43\textwidth}
    \begin{center}
      Temperature at the exam dates
    \end{center}
    \begin{figure}[h]
      \centering
      \includegraphics[width = \textwidth]{../Output/images/reg_pre10_exam_4.pdf}
    \end{figure}
  \end{minipage}
  \begin{minipage}{0.43\textwidth}
    \begin{center}
      Average temperature for 10 days before the exam
    \end{center}
    \begin{figure}[h]
      \includegraphics[width = \textwidth]{../Output/images/reg_pre10_pre10_4.pdf}
      \centering
    \end{figure}
  \end{minipage}
  \tiny
  \begin{tablenotes}
  \item Notes;
    The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
    In the left figure, the estimates on the temperature on the exam dates are shown.
    In the right figure, the estimates on the average temperature for 10 days before the exam are shown.
    Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
    Each interval on the x-axis does not include the right end.
    The 90\% confidence intervals are shown.
    Prefecture fixed effects and year fixed effects are also included.
    Standard errors are clustered at the prefecture level.
  \end{tablenotes}
\end{frame}

\begin{frame}\frametitle{{\normalsize Effects of other weather variables on the matriculation shares (\%)} \\ {\small Cumulated snow on the exam date matters}}
  \begin{table}[h]
    \Wider[4em]{
    \center
    \fontsize{7}{5}\selectfont
    \input{../Output/tex/reg_pre10_beamer.tex}
    \tiny
    \begin{tablenotes}
    \item 
      The outcome variable is the matriculation shares (\%) for the University of Tokyo from each prefecture.
      The matriculation share is calculated based on the ratio of the number of students from high schools in the prefecture to the total number of matriculation.
      Standard errors are clustered at the prefecture level.
    \end{tablenotes}
  }
  \end{table}
\end{frame}

\begin{frame}\frametitle{Some additional analysis: Female vs. Male \\ {\small Female students are less affected by temperature\dots or maybe not?}}
  \begin{figure}
    \center
    \begin{minipage}{0.43\textwidth}
      \begin{center}
        Female \\
        {\small (mean: 0.38 \%, median: 0.13 \%)}
      \end{center}
      \begin{figure}[h]
        \centering
        \includegraphics[width = \textwidth]{../Output/images/reg_gender_2.pdf}
      \end{figure}
    \end{minipage}
    \begin{minipage}{0.43\textwidth}
      \begin{center}
        Male \\
        {\small (mean: 1.70 \%, median: 0.61 \%)}
      \end{center}
      \begin{figure}[h]
        \includegraphics[width = \textwidth]{../Output/images/reg_gender_4.pdf}
        \centering
      \end{figure}
    \end{minipage}
    \tiny
    \begin{tablenotes}
    \item Notes;
      The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
      In the left figure, the outcome is the matriculation share of female students from each prefecture.
      In the right figure, the outcome is the matriculation share of male students from each prefecture.
      Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
      Each interval on the x-axis does not include the right end.
      The 90\% confidence intervals are shown.
      Prefecture fixed effects and year fixed effects are also included.
      Standard errors are clustered at the prefecture level.
    \end{tablenotes}
  \end{figure}
\end{frame}

\begin{frame}\frametitle{Some additional analysis: Humanity vs. Science \\ {\small No significant difference in temperature effects}}
  \begin{figure}
    \center
    \begin{minipage}{0.43\textwidth}
      \begin{center}
        Humanity \\
        {\small (mean: 2.07 \%, median: 0.76 \%)}
      \end{center}
      \begin{figure}[h]
        \centering
        \includegraphics[width = \textwidth]{../Output/images/reg_major_2.pdf}
      \end{figure}
    \end{minipage}
    \begin{minipage}{0.43\textwidth}
      \begin{center}
        Science \\
        {\small (mean: 2.09 \%, median: 0.76 \%)}
      \end{center}
      \begin{figure}[h]
        \includegraphics[width = \textwidth]{../Output/images/reg_major_4.pdf}
        \centering
      \end{figure}
    \end{minipage}
    \tiny
    \begin{tablenotes}
    \item Notes;
      The figures show the regression coefficients of the matriculation shares for UTokyo (\%) on temperature bins.
      In the left figure, the outcome is the matriculation share to humanity major from each prefecture.
      In the right figure, the outcome is the matriculation share to science major from each prefecture.
      Rainfall and cumulated snow on the ground (both on the exam days and average for 10 days before the exam) are included in the regression.
      Each interval on the x-axis does not include the right end.
      The 90\% confidence intervals are shown.
      Prefecture fixed effects and year fixed effects are also included.
      Standard errors are clustered at the prefecture level.
    \end{tablenotes}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
  \begin{itemize}
    \item Weather on the exam dates affects the matriculations for UTokyo
      \begin{itemize}
        \item A decrease in temperature from 3-6 \degree C to $<$0 \degree C decreases the probability of matriculation by 0.18 percentage points \\
          (9\% of the average and 22\% of the median matriculation shares)
        \item Snow on the ground cumulated more than 10cm decreases the probability of matriculation by 0.11 percentage points \\
          (5\% of the average and 13\% of the median matriculation shares)
      \end{itemize}
    \item Suggests that exam performance is negatively affected by winter weather
      \begin{itemize}
        \item Low temperature in the morning or during the exam negatively affects cognitive ability?
        \item Snow on the ground makes feet wet, which further decreases body temperature?
        \item Cumulated snow increases the risk of transportation delays?
      \end{itemize}
    \item Implications for university admissions process:
      \begin{itemize}
        \item Use other information such as extracurricular activities and personal statements for university admission?
        \item Adjust weights for Center Test and the second-stage exam?
      \end{itemize}
  \end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Deviation of temperatures from within-prefecture averages \\ {\small Large variation in deviation of temperatures even within each year}} 
  \label{temp_dev_2}
  \begin{center}
    \begin{figure}
      %\caption{Map of matriculation shares (\%)}
      \includegraphics[width=6.2cm]{../Output/images/temperature_diff_by_year.pdf}
      \tiny
      \begin{tablenotes}
      \item Notes:
        Temperature at prefecture capitals between 6 AM and 6 PM on days of Center Test is used.
        Deviations of average temperatures across two test days from their within-prefecture means are shown in the figure by year.
        In each panel, red dots are the deviations in the year shown above and gray dots are the deviations in the other years.
        The prefectures are ordered by the mean temperature across years (lowest to left and highest to right). \\
      \item 
        \hyperlink{est_eq}{\beamergotobutton{Estimation equation}}
      \end{tablenotes}
    \end{figure}
  \end{center}
\end{frame}

### 2021-05-12 Writeups/paper.tex
Revised slides for presentation

I use the weather on the dates of Center Test and investigate its effect on the matriculation for the University of Tokyo (UTokyo henceforth).
UTokyo is a national university and known to be the most prestigious in Japan.\footnote{
  According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
  The second highest-ranked university in Japan is Kyoto University, which is 125th ranked in the world ranking.
}
This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.

The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
The estimates are not only statistically but also economically significant.
Changing the temperature on the exam dates from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admission process.

@@

After Center Test, applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students physically go to the universities and take the exam.
Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
UTokyo has the second-stage exam at the end of February for two days.\footnote{
  Until 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admission process for those students. 
}

@@

I analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
The reason why I use the matriculation share for UTokyo is as follows:
consider a matriculation share for a middle-ranked university.
Suppose also that low temperature has a negative impact on exam scores.
Then, 
(i) students in the prefecture who would get into the middle-ranked university if the temperature was higher could go to a lower-ranked university, but
(ii) students in the prefecture who would get into a higher-ranked university may get into the middle-ranked university.
Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
}
Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at Center Test.

In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
%Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
%I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
The main right-hand side variable is temperature on the exam dates.
To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals, $T_{jt}^k$.\footnote{
  The results with a linear specification are shown in Appendix \ref{sec:appendix_table} and will be discussed below.
}
I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

@@

In column (2), I add rainfall and snowfall in the regressions.
While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
In column (3), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage point.
These results suggest that not only temperature but also snow on the ground on the exam dates affect exam performance.

@@

The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage point.

The results in this study have implications for the admission process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
Also, universities may adjust the weights for Center Test and the second-stage exam.
Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of exam results for later life outcomes of students, it is desirable that universities take measures to mitigate the effect of seemingly irrelevant factors on admission.

>>>>

I use the weather on the dates of Center Test and investigate its effect on matriculation for the University of Tokyo (UTokyo henceforth).
UTokyo is a national university and known to be the most prestigious in Japan.\footnote{
  According to \citet{usnews}, UTokyo is the highest-ranked university in Japan (73rd ranked in the world ranking).
  The second highest-ranked university in Japan is Kyoto University, which is 125th ranked in the world ranking.
}
This allows me to attribute a reduction in matriculation shares to the worse exam performance, instead of the better performance which could induce students to choose better universities.

The econometric analyses show that low temperature and snow cumulated on the ground on exam dates reduce the matriculation share.
The estimates are not only statistically but also economically significant.
Changing the temperature on the exam dates from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share by 0.18\%, which amounts to 9\% of the average or 22\% of the median matriculation shares.
The results provide implications for effective measures to be taken to mitigate the negative impact of winter weather.
These include preparing waiting rooms for exam takers to warm up for equalizing their pre-exam conditions or adjusting the importance of the scores at Center Test in the admissions process.

@@

After Center Test, applicants for public universities typically take the second-stage exam.
This exam is made by each university, and students physically go to the universities and take the exam.
Therefore, every applicant for a university takes the second-stage exam at the same location on the same days.
UTokyo has the second-stage exam at the end of February for two days.\footnote{
  Until 2015, UTokyo had another second-stage exam in March and a small number of exam takers got admitted through the exam (around 3\% of all admitted students).
  In 2016, UTokyo abolished the March exam and instead started to admit the small number of students recommended by their high schools based on interviews and scores at Center Test (around 2\% of all admitted students).
  Since the majority of students are admitted through the second-stage exam in February, below I focus on the admissions process for those students. 
}

@@

I analyze the effect of temperature and other weather variables on exam dates on the matriculation share for UTokyo.
The reason why I use the matriculation share for UTokyo is as follows:
consider a matriculation share for a middle-ranked university.
Suppose also that low temperature has a negative impact on exam scores.
Then, 
(i) students in the prefecture who would have gotten into the middle-ranked university if the temperature were higher may end up in a lower-ranked university instead, but
(ii) students in the prefecture who would have gotten into a higher-ranked university may end up in the middle-ranked university instead.
Hence, the matriculation share of the prefecture for the middle-ranked university may not be affected by low temperature.
However, the second effect is unlikely to be large for UTokyo since it is known to be the best university in Japan.\footnote{
  \citet{Kawaguchi2008} describes that ``The University of Tokyo has occupied the top position of the single-peaked university hierarchy since its establishment in 1877.''
}
Therefore, I rule out the second possibility and attribute a reduction in matriculation shares to the worse performance at Center Test.

In the analyses, the outcome variable, $Y_{jt}$, is the matriculation share (\%) for UTokyo of a prefecture $j$ in year $t$.
%Let $T_{jt}$ be the average temperature across two exam dates in $j$ in year $t$.
%I use functions of $T_{jt}$ in the regressions ($f$), which can be linear or non-linear.
The main right-hand side variable is temperature on the exam dates.
To allow for non-linear effects of temperature on the outcome, I use the 3-$^o$C temperature intervals.\footnote{
  The results with a linear specification are shown in Appendix \ref{sec:appendix_table} and will be discussed below.
}
Let $T_{jt}^k$ represent the $k$'th temperature bin.
I also include other weather variables such as rainfall, snowfall, and cumulated snow on the ground on exam dates as a vector $X_{jt}$.
As fixed effects, prefecture fixed effects ($\mu_j$) and year fixed effects ($\tau_t$) are used.
Finally, the error term is represented as $\epsilon_{jt}$.

@@

In column (2), I add rainfall and snowfall in the regressions.
While temperature coefficients are barely affected, I find that rainfall and snowfall on the exam dates do not impact the matriculation shares.
In column (3), instead of snowfall on the exam dates, I use cumulated snow on the ground and find its negative impact on the outcome. 
To capture the effect of the existence of a certain amount of snow on the ground, column (4) allows a non-linear effect of cumulated snow.
The result shows that snow on the ground cumulated more than 10 cm ($\approx$ 4 inches) decreases the matriculation share by 0.11 percentage points.
These results suggest that not only temperature but also snow on the ground on the exam dates affect exam performance.

@@

The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage points, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage points.

The results in this study have implications for the admissions process of universities.
Recognizing the limitation to measure students' cognitive ability through an exam affected by external factors such as weather, universities may use other measures to select students.
Examples include extracurricular activities and personal statements, which are actively utilized in other countries such as the United States.
Also, universities may adjust the weights for Center Test and the second-stage exam.
Since the second-stage exams are held at each university, all exam takers are exposed to similar environments.
This rules out the possibility that exam takers at different places are affected differently by their conditions.
Given the importance of exam results for later life outcomes of students, it is desirable that universities take measures to mitigate the effect of seemingly irrelevant factors on admission.
